Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-12 research_class/paper.tex
Plural -> singular sentence.
This sentence is too complex to be plural; subject/verb agreement would require
a few changes and more complex wording. I think it's clearer and simpler in the
singular.

In order to ensure that each state machine on every node executes
exactly the same commands in exactly the same order, the Raft system
provides safety guarantees. In particular, there are some restrictions
on which Raft nodes are actually eligible to become a leader based on
the state of their transaction log compared to other node transaction
logs. A Raft node will only vote for a candidate if the candidate has
a log that is more up-to-date than the voter. A log entry with a later
term is always more up-to-date. If the log entries have the same term,
then the entry with a higher index is more up-to-date. In addition,
Raft leaders may not consider entries from a previous term to be
committed until it has committed at least one entry from its own
term
\cite[Section~3.6]{raft_thesis:ongaro14}.

>>>>

In order to ensure that each state machine on every node executes
exactly the same commands in exactly the same order, the Raft system
provides safety guarantees. In particular, there are some restrictions
on whether a Raft node is actually eligible to become a leader, based on
the state of its transaction log compared to other node transaction
logs. A Raft node will only vote for a candidate if the candidate has
a log that is more up-to-date than the voter. A log entry with a later
term is always more up-to-date. If the log entries have the same term,
then the entry with a higher index is more up-to-date. In addition,
Raft leaders may not consider entries from a previous term to be
committed until it has committed at least one entry from its own
term
\cite[Section~3.6]{raft_thesis:ongaro14}.
